### 2018-04-30 paper/design.tex
up
wrote a bit and experiments are undergoing

\section{Design of the \name file exchange system}

This section presents the \name protocol in detail.
Our goal is to enable private and reliable file exchange between users participating in the system, by using their respective devices only.
When Alice and Bob, two users of our system, want to exchange a file $f$ through \name; they start by sharing some information out-of-band, e.g. from their smartphones.
More precisely, they exchange metadata on $f$, encryption keys, and agree upon a Predictive Onion Route (POR).
PORs are our adaptation of onion routes, allowing secret communication between two entities despite the unreliability of the nodes that relay their messages.
From there on, Alice and Bob add the POR information to the headers of their subsequent file exchange messages, such that the file transfer remains secret to anyone but them.

@@

The privacy objectives of our system require encryption primitives that we first detail in section~\ref{BuildingBlocks}. The other constituents of \name are depicted in figure~\ref{fig:outline}.
On top, the devices of each user are circled in gray, and form a user's device squad. The squad online members communicate among themselves: they exchange files and messages information, and cooperate to predict the user's future behavior. 
This first protocol is called the \emph{Squad Overlay} and will be discussed in section~\ref{sec:squad_overlay}.
%On top we see that each user's devices (shown as clouds) communicate with one another through a dissemination protocol---coined the \emph{squad overlay}---that will be discussed in section~\ref{sec:squad_overlay}. 
Below, we see all devices connected in a random graph: each device gives information about itself to random nodes when it is online. 
This \emph{Global Overlay} will be covered in section~\ref{sec:global_overlay}.
The information brought by these overlays allows devices to securely and reliably exchange messages between users by creating PORs, as will be explained in section~\ref{sec:message_passing}.
Given this message passing protocol, users can privately exchange files, as shown in the bottom of the figure. We will cover this ultimate goal in section~\ref{sec:file_exchange}.

\include*{building-blocks}
\include*{squad-overlay-design}
\include*{global-overlay-design}
\include*{message-passing-design}
\include*{file-exchange-design}

>>>>

\section{Design of the \name file exchange system}
\label{design}
This section presents the \name protocol in detail.
Our goal is to enable private and reliable file exchange between users participating in the system, by using their respective devices only.
When Alice and Bob, two users of our system, want to exchange a file $f$ through \name; they start by sharing some information out-of-band, e.g. from their smartphones.
More precisely, they exchange metadata on $f$, encryption keys, and agree upon a Predictive Onion Route (POR).
PORs are our adaptation of onion routes, allowing secret communication between two entities despite the unreliability of the nodes that relay their messages.
From there on, Alice and Bob add the POR information to the headers of their subsequent file exchange messages, such that the file transfer remains secret to anyone but them.

@@

The privacy objectives of our system require encryption primitives that we first detail in section~\ref{BuildingBlocks}. The other constituents of \name are depicted in figure~\ref{fig:outline}.
On top, the devices of each user are circled in gray, and form a user's device squad. The squad online members communicate among themselves: they exchange files and messages information, and cooperate to predict the user's future behavior. 
This first protocol is called the \emph{Squad Overlay} and will be discussed in section~\ref{sec:squad_overlay}.
%On top we see that each user's devices (shown as clouds) communicate with one another through a dissemination protocol---coined the \emph{squad overlay}---that will be discussed in section~\ref{sec:squad_overlay}. 
Below, we see all devices connected in a random graph: each device gives information about itself to random nodes when it is online. 
This \emph{Global Overlay} will be covered in section~\ref{sec:global_overlay}.
The information brought by these overlays allows devices to securely and reliably exchange messages between users by creating PORs, thus enabling file exchange between users, as will be explained in section~\ref{sec:message_passing}.
%Given this message passing protocol, users can privately exchange files, as shown in the bottom of the figure. We will cover this ultimate goal in section~\ref{sec:file_exchange}.

\include*{building-blocks}
\include*{squad-overlay-design}
\include*{global-overlay-design}
\include*{message-passing-design}
%\include*{file-exchange-design}

### 2018-04-30 paper/message-passing-design.tex
wrote a bit and experiments are undergoing

\NewAlgorithm{\Fwd}{Forward}
\NewAlgorithm{\Send}{BuildRouteS}
\NewAlgorithm{\Recv}{BuildRouteR}
\NewAlgorithm{\ExtendRoute}{ExtendRoute}
\NewAlgorithm{\CreateOnionLayer}{CreateLayer}
\NewAlgorithm{\Dec}{Dec}
\NewAlgorithm{\Store}{Store}
\NewVariable{\sk}{sk}
\NewVariable{\rdv}{rdv}
\NewVariable{\LRV}{\mathcal{L_{RV}}\xspace}
\NewVariable{\Hsend}{\mathcal{H}_{\text{send}}\xspace}
\NewVariable{\Hrec}{\mathcal{H}_{\text{rec}}\xspace}
\NewVariable{\Hforward}{\mathcal{H}_f\xspace}
\NewVariable{\Hbackward}{\mathcal{H}_b\xspace}
\NewVariable{\Hsendforward}{\mathcal{H}_{\text{send f}}\xspace}
\NewVariable{\Hsendbackward}{\mathcal{H}_{\text{send b}}\xspace}
\NewVariable{\Hrecforward}{\mathcal{H}_{\text{rec f}}\xspace}
\NewVariable{\Hrecbackward}{\mathcal{H}_{\text{rec b}}\xspace}
%\NewVariable{\nfilechunks}{\#\text{chunks}}

@@

When Alice wants to send a file to Bob, they first have to call the route building algorithm, and to exchange relevant information out of band (e.g. using mail, or their phones' bluetooth connection).
They create a route of $L$ layers, a configuration parameter that must be odd. We introduce $l=(L-1)/2$.

@@

Once Alice get the \(H_\rdv\), Alice uses \(\Send\) at some
later time to send the message to Bob using any of her devices from
its \squad.% (See \cref{SPORSend}). 
First, \(\Send\) extends the route
\(H_\rdv\) with some hops of Alice's choosing (uniformly randomly
chosen). Second, \(\Send\) extracts from the onion the first
layer, which contained the overall
possible rendez-vous points $D$ previously selected by the recipient (i.e. Bob).
One device from $D$ is randomly chosen, and the \(\Fwd\)
sub-function is called as long as the message forwarding to one node of
the next layer is not successful.% (See \cref{SPORFwd}). 
Along the path, each node decrypts
in sequence the different layer with the current node’s private key. 
The end of the route is reached when special value \(H_\rdv = \top\) is
encountered. Consequently the ciphered message \(c_m\) is then stored
in the disk of the local node through the \(\Store\) sub function.%(\cref{SPORRecv}).

\david{the use of DeBE algorithms must be explicitly explained here}

@@

>>>>

\NewAlgorithm{\Fwd}{Forward}
\NewAlgorithm{\Send}{BuildRouteS}
\NewAlgorithm{\Recv}{BuildRouteR}
\NewAlgorithm{\ExtendRoute}{ExtendRoute}
\NewAlgorithm{\CreateOnionLayer}{CreateLayer}
\NewAlgorithm{\Dec}{Dec}
\NewAlgorithm{\Store}{Store}
\NewVariable{\sk}{sk}
\NewVariable{\rdv}{rdv}
\NewVariable{\LRV}{\mathcal{L_{RV}}\xspace}
\NewVariable{\Hsend}{\mathcal{H}_{\text{send}}\xspace}
\NewVariable{\Hrec}{\mathcal{H}_{\text{rec}}\xspace}
\NewVariable{\Hforward}{\mathcal{H}_f\xspace}
\NewVariable{\Hbackward}{\mathcal{H}_b\xspace}
\NewVariable{\Hsendforward}{\mathcal{H}_{\text{send f}}\xspace}
\NewVariable{\Hsendbackward}{\mathcal{H}_{\text{send b}}\xspace}
\NewVariable{\Hrecforward}{\mathcal{H}_{\text{rec f}}\xspace}
\NewVariable{\Hrecbackward}{\mathcal{H}_{\text{rec b}}\xspace}
\NewVariable{\datakey}{k_{\text{data}}\xspace}
%\NewVariable{\nfilechunks}{\#\text{chunks}}

\david{the use of DeBE algorithms must be explicitly explained in this section}

@@

\commentAL{A symmetric key \datakey should be exchanged during this step, to encrypt the data}

When Alice wants to send a file $f$ to Bob, they first have to call the route building algorithm, and to exchange relevant information out of band (e.g. using mail, or their phones' bluetooth connection).
They create a route of $L$ layers, a configuration parameter that must be odd. We introduce $l=(L-1)/2$.

@@

% Alice uses \(\Send\) at some
% later time to send the message to Bob using any of her devices from
% its \squad.% (See \cref{SPORSend}). 
% First, \(\Send\) extends the route
% \(H_\rdv\) with some hops of Alice's choosing (uniformly randomly
% chosen). Second, \(\Send\) extracts from the onion the first
% layer, which contained the overall
% possible rendez-vous points $D$ previously selected by the recipient (i.e. Bob).
% One device from $D$ is randomly chosen, and the \(\Fwd\)
% sub-function is called as long as the message forwarding to one node of
% the next layer is not successful.% (See \cref{SPORFwd}). 
% Along the path, each node decrypts
% in sequence the different layer with the current node’s private key. 
% The end of the route is reached when special value \(H_\rdv = \top\) is
% encountered. Consequently the ciphered message \(c_m\) is then stored
% in the disk of the local node through the \(\Store\) sub function.%(\cref{SPORRecv}).

@@

\subsubsection{Exchanging a file} % (fold)
\label{ssub:exchanging_a_file}

% subsubsection exchanging_a_file (end)
\newcommand{\messagesize}{\ensuremath{s_m}}
\newcommand{\filesize}{\ensuremath{s_f}}
\newcommand{\headersize}{\ensuremath{s_{\mathcal{H}}}}

Once Alice get the \Hforward, she can start sending her file $f$ to Bob. 
To do so, she chunks it to pieces, and iteratively send the chunks to Bob, that replies with an acknowledgment (ACK) for that chunk.
Once all chunks have been acknowledged, Alice sends an empty message to Bob, signifying transfer termination.

To prevent \name from message size analysis attacks, the messages have a fixed size \messagesize.
As shown in the previous section~\ref{ssub:building_routes}, headers have a variable size \headersize per route (but \Hforward remains constant once the POR is established).
For this reason, file chunks have a fixed size per session: $\filesize = \messagesize - \headersize$.

A message payload is composed of the following information:

\begin{itemize}
  \item An identifier for the file;
  \item The chunk ID, that identifies its position in $f$;
  \item The file chunk;
  \item An error correction code (e.g. a SHA-1 hash of the chunk, à la BitTorrent\cite{bt_bep3}).
\end{itemize}

Payloads are encoded using \datakey that was shared between Alice and Bob during route creation \commentAL{Not done}.

% We are interested in transferring large files.
% Every device \(d\in D\) in the global device swarm is only periodically online.
% We will thus divide the data to send into \(n\) smaller chunks (similar to 
% BitTorrent~\cite{BitTorrent}).
% The idea is to choose \(n\) such that each chunk will be small enough to be 
% successfully relayed by a device before it goes offline again.
% The chunk size is empirically determined in \cref{Performance}.
% \commentDaniel{Adrien, is that true?}

% As stated above, Alice and Bob exchange some limited data out-of-bound using 
% their smartphones.
% The information they will exchange is the following:
% \begin{enumerate}
%   \item Bob creates an onion route header, \(H_\rdv\), by running 
%     \([\Recv]\) %(\cref{SPORRecv}) 
%     and gives it to Alice.
%   \item Alice gives Bob number of file chunks, \(n\), and the size of the file 
%     chunks.
%   \item They agree on a file-specific key \(k\) for some (authenticated) 
%     encryption scheme \(\Enc*\).
% \end{enumerate}
% Then Alice encrypts the file \(f\) and receives the ciphertext \(c_f\gets 
%   \Enc*[Enc](k, f)\).
% She then divides \(c_f\) into \(n\) chunks, \(c_f^{(1)}, \dotsc, c_f^{(n)}\), 
% and runs \(\Send(H_\rdv, c_f^{(i)})\) for all \(1\leq i\leq n\) in 
% parallel.
% \commentDaniel{Or shall we do it sequentially?}
